\vspace{-1.5em} \bf A general and efficient representation of ancestral recombination graphs

### 2023-10-12 paper.tex
Tweak
Pass at locally unary nodes section

A genome ARG (gARG) is a graph in which nodes represent
haploid genomes and edges represent
genetic inheritance between an ancestor and a descendant.
% This has two purposes: clarify that we're not talking about Shipilina
% et als edges, and also get "Graph theory" in here
(Note that we are using the term ``edge'' in its standard
graph-theoretic sense
and not the specialised interpretation of
\cite{shipilina2023origin}.)
The topology of a gARG specifies that genetic inheritance
occurred between particular
ancestors and descendants, but the graph connectivity
does not tell us which \emph{parts} of their genomes were inherited.
In order to capture the effects of recombination
(and other processes that lead to the partial genome inheritance)
 we ``annotate'' the edges with the genome
coordinates over which inheritance occurs.
We can define a gARG formally as follows.
Let $N \subset \mathbb{N}$ be the set of nodes representing
the genomes in the gARG, and $E$ be the set of edges.
We will usually define a set of nodes $S \subseteq N$
representing the sampled genomes
(but see section XXX for some subtlety around this point).
Each element of $E$ is a tuple $(c, p, I)$ such that $c, p \in N$ are the child and
parent nodes and $I$ is the set of disjoint genomic intervals
%$[\ell, r)$
over
which genome $c$ inherits from $p$. Thus, each topological connection between
 a parent and child in the graph is ``annotated'' with set of
inheritance intervals $I$.

\begin{figure}
\begin{center}
    \includegraphics[width=\textwidth]{illustrations/arg-in-pedigree}
\end{center}
\caption{\label{fig-arg-in-pedigree}
% TODO caption needs another pass. One the full section has been written
% it'll be clearer what we need to say in the caption vs the text.
An example genome ARG embedded in a pedigree.
(A) Diploid individuals, visualised in a highly inbred pedigree and
labelled $D_1$ to $D_8$,
contain both paternal and maternal  genomes
labelled \textsf{a} to \textsf{p}. Black lines show inheritance paths connecting
genomes in the current generation (\textsf{a} to \textsf{d}) with their ancestors.
Genomes \textsf{a} and \textsf{c} are the product of two independent
recombination events between
the paternal genomes \textsf{e}
and \textsf{f} (with breakpoints in red), and regions of genome inherited are shown.
Genomes are shaded such that where, backwards in time,
they merge into a common ancestor, the merged region is darker.
(B) The corresponding gARG along with inheritance annotations on all edges
(partial inheritance in bold).
(C) The corresponding local trees.
}
\end{figure}

As illustrated in Fig.~\ref{fig-arg-in-pedigree},
the gARG for a given set of individuals is embedded in their pedigree.
In this diploid example, each genome is inherited from one
of the individual's parents,
and may be the recombined product of that parent's two genomes.
For example, diploid individual $D_1$ in Fig.~\ref{fig-arg-in-pedigree}
has two genomes \noderef{a} and \noderef{b},
inherited from parents $D_3$ and $D_4$.
Genome \noderef{b} was inherited directly from $D_4$'s genome \noderef{g} without
recombination, whereas
\noderef{a} is the recombinant product of
$D_2$'s two genomes \noderef{e} and \noderef{f} crossing over at position 2.
This recombination means \noderef{a} inherits the (half-closed) genome
interval $[0, 2)$ from \noderef{e} and $[2, 10)$ from \noderef{f}.
These intervals are shown attached to the corresponding graph edges.

@@

% NOTE: important to emphasise TWO things here, events and vagueness
% actual encoding mechanism (i.e. how trees fit into the ARG)
A common feature of these definitions is that they are expressed
in terms of evolutionary \emph{events}, and so for the purposes of
discussion we can label
this prevailing interpretation as an ``event ARG'', or eARG.
(Many definitions also emphasise
the necessity of exhaustively capturing \emph{all} events, which we
examine in later sections.)
Another common feature of these definitions is that they do not explicitly
discuss the mechanism by which genealogical trees vary along the genome.
The topology of an eARG defines the common ancestor and
recombination events that occurred,
but the graph structure alone is not sufficient to define the local trees,
or equivalently, how ``ancestral material'' (Section XXX) flows along
the edges of the ARG.
This is usually assumed to follow the mechanism described by
Griffiths and colleagues in which we have
two different ``types'' of node in the graph:
common ancestor nodes in which the inbound lineages are merged into a
single ancestral lineage with one parent, and recombination
nodes in which a single lineage is split into two independent
ancestral lineages.
Recombination nodes are then
annotated with
the corresponding crossover breakpoint~\citep{griffiths1996ancestral}.
Fig.~\ref{fig-arg-data-structure} shows an example of a classical
eARG with three samples (\noderef{a}, \noderef{b}, and \noderef{c})
and a single recombination event, along with an example concrete
encoding of the data.  There is a single recombination event
at node \noderef{d} with a breakpoint at position $x$. We
assume that \noderef{d} inherits genetic material to the
left of $x$ from \noderef{e} and to the right of $x$ from \noderef{f}.
As shown in Fig.~\ref{fig-arg-data-structure}B,
the local trees are embedded in the graph, and can be reconstructed
in essentially the same manner as outlined the previous section for
gARGs. The only difference is that decisions about which outbound
edge to follow during the rootward traversal are taken at recombination
nodes, following
either the common convention that the order of parents
is significant~\citep[e.g.][]{griffiths1991two},
or by incorporating additional information to
distinguish left and right parents
into the
encoding~\citep[e.g.][]{gusfield2014recombinatorics,ignatieva2021kwarg}.

@@

\end{tikzpicture}
\caption{\label{fig-arg-data-structure}
A classical event ARG. (A) Standard graph depiction with
breakpoint $x$ associated with the recombination node \noderef{d}.
Nodes \noderef{e}, \noderef{f} and \noderef{g} are common ancestor events.
(B) Corresponding local trees to the left and right of breakpoint $x$
(note these are shown in the conventional form in which only coalescences
within the local tree are included; see section XXX for a discussion
of this important point).
(C) A concrete encoding of the information (right).
Recombination nodes have a non-null breakpoint
and two parents.
}
\end{figure}

Whether we regard nodes as events or genomes is something of a
philosophical question, and in most senses the two are equivalent
(but see the discussion on ``unary nodes'' in section XXX).
From a concrete data-structure encoding perspective, the only real
difference between an eARG and a gARG is that we store recombination
\emph{breakpoints} at nodes of out-degree two (recombination nodes)
in an eARG and we store \emph{inheritance intervals} on the edges
of a gARG. A key advantage of associating inheritance intervals with
edges in a gARG is that it allows us to describe evolutionary events other
than simple crossovers, such as multiple recombinations and
gene-conversions. By explicitly stating the exact regions of genome
that are transmitted along an edge, we generalise the representation
to encompass any process that leads to the differential inheritance of
genetic material along the genome.

@@

Prospective ARGs arise in individual-based forwards-time
simulations~\citep{kelleher2018efficient,haller2018tree},
where the genetic inheritance between genomes is recorded
exhaustively and periodically
``simplified'' to retain only
the ancestry relevant to the current population.
\citet{kelleher2018efficient} refer to the structure
recording all such forwards-in-time genetic relationships
as an ``embellished pedigree`` (and suggest the term ``nedigree'' as a shorthand).
Describing this instead as a ``prospective ARG'', emphasising
the use of the same data structures and the direct connection with
the usual retrospective interpretation of an ARG, may be
more useful.
The ``simplify'' algorithm, which prunes away parts of the graph that
are not ancestral to a sample, is the key enabling factor for
this approach to forwards-time simulation and is
described in detail by
\citet{kelleher2018efficient}.
It is a powerful tool for simulation and analysis, as it
allows to efficiently subset ARGs both in terms of the
samples and levels of detail about recombination retained,
as we discuss in the following sections.

@@

It is useful to have
a concrete definition and explicit process for local tree extraction.
We can describe a local tree as an
oriented tree~\cite[p.\ 461]{knuth11combinatorial},
a sequence of integers $\pi_1\pi_2\dots$ where $\pi_u$ denotes the parent of
node $u$~\citep{kelleher2013coalescent,kelleher2014coalescent,kelleher2016efficient}.
If $u$ is a root
% I'm not sure if this reachability stuff is a helpful clarification, and whether it'll just
% confuse people. It depends on some tricky details.
(or not reachable from the samples)
in the local tree at position $x$, then $\pi_u = -1$ (by convention).
% JK: this confused some people, so best left out?
% Technically, this structure is a ``forest'', as it allows us to have
% multiple disconnected trees, which occurs when all samples have not
% found a most recent common ancestor.
Oriented trees allow nodes
to have  any number of children; from one (see section XXX for more
discussion on such ``unary nodes'' in the local trees), to arbitrarily
large polytomies.
To recover the local tree $\pi$ at position $x$, we begin by
setting $\pi_u = -1$ for each $u\in N$. Then, for each sample
node in $S$ we trace its path rootwards through the
ARG for position $x$, and record this path in $\pi$.
Specifically, at a given node $u$,
we an find edge $(c, p, I) \in E$ such that $u = c$ and $x \in I$, and set
$\pi_c \leftarrow p$. We then set $u \leftarrow p$, and repeat
until either $\pi_u \neq -1$ (indicating we have traversed this section
of the ARG already on the path from another sample) or there
is no matching outbound edge (indicating we are at a root).

@@

The internal nodes of trees, however, are usually
considered to be \emph{unlabelled},
because they most often correspond
to anonymous hypothetical ancestors.
Internal ARG nodes likewise correspond to anonymous hypothetical
ancestors, but if we do not label them we lose the fact that
the \emph{same} ancestors persist across multiple trees.
Without labelled internal tree nodes,
we must infer their identity
from the tree topology, which is both
expensive to compute and imprecise. For example
we could infer that node \textsf{k} is shared in the second
and third trees of in Fig.~\ref{fig-simplification}D
because it subtends identical subtrees in both,
but it would not be straightforward to infer that it
is also the root of the first tree.

\cite{shipilina2023origin} discuss the same ideas,
and note that the
``full ARG...~contains more information than the series of tree
sequences along the genome''.
Their statement that an ARG
contains more information than its local trees is true only if
the local trees are unlabeled and/or do not contain unary nodes.
However, as we have shown, if the local trees
contain labelled internal (possibly unary) nodes,
then  there is precisely as
much information in them as an ARG.
Whether such unary nodes are \emph{observable}
is an entirely separate question, of course.

@@

@@

\begin{figure}[ht]
\centering
% FIXME this is a quick nasty hack to make the figure a bit smaller and
% prevent flushing all the other figures to the end of the document.
\scalebox{0.54}{
\begin{tabular}{cc}
\begin{tikzpicture}
	\node [anchor=north west] at (-3.5,9.3) {\LARGE \textbf{A}};
	\draw (-0.4, -0.2) -- (0.4, -0.2) -- (0.4, -0.3) -- (-0.4, -0.3) -- (-0.4, -0.2);
	\draw (-0.1, -0.1) -- (-0.1, -0.4);
	\node [label=below:{\small $v$}] at (-0.1, -0.2) {};
	\draw (3.6, -0.2) -- (4.4, -0.2) -- (4.4, -0.3) -- (3.6, -0.3) -- (3.6, -0.2);
	\draw (5.6, -0.2) -- (6.4, -0.2) -- (6.4, -0.3) -- (5.6, -0.3) -- (5.6, -0.2);

>>>>

A genome ARG (gARG) is a directed acyclic graph in which nodes represent
haploid genomes and edges represent
genetic inheritance between an ancestor and a descendant.
% This has two purposes: clarify that we're not talking about Shipilina
% et als edges, and also get "Graph theory" in here
(Note that we are using the term ``edge'' in its standard
graph-theoretic sense
and not the specialised interpretation of
\cite{shipilina2023origin}.)
The topology of a gARG specifies that genetic inheritance
occurred between particular
ancestors and descendants, but the graph connectivity
does not tell us which \emph{parts} of their genomes were inherited.
In order to capture the effects of recombination
(and other processes that lead to the partial genome inheritance)
 we ``annotate'' the edges with the genome
coordinates over which inheritance occurs.
We can define a gARG formally as follows.
Let $N \subset \mathbb{N}$ be the set of nodes representing
the genomes in the gARG, and $E$ be the set of edges.
We will usually define a set of nodes $S \subseteq N$
representing the sampled genomes
(but see section XXX for some subtlety around this point).
Each element of $E$ is a tuple $(c, p, I)$ such that $c, p \in N$ are the child and
parent nodes and $I$ is the set of disjoint genomic intervals
%$[\ell, r)$
over
which genome $c$ inherits from $p$. Thus, each topological connection between
 a parent and child in the graph is ``annotated'' with set of
inheritance intervals $I$.

\begin{figure}
\begin{center}
    \includegraphics[width=\textwidth]{illustrations/arg-in-pedigree}
\end{center}
\caption{\label{fig-arg-in-pedigree}
% TODO caption needs another pass. One the full section has been written
% it'll be clearer what we need to say in the caption vs the text.
An example genome ARG embedded in a pedigree.
(A) Diploid individuals (blue), visualised in a highly inbred pedigree and
labelled $D_1$ to $D_8$,
contain both paternal and maternal  genomes
labelled \textsf{a} to \textsf{p}. Black lines show inheritance paths connecting
genomes in the current generation (\textsf{a} to \textsf{d}) with their ancestors.
Genomes \textsf{a} and \textsf{c} are the product of two independent
recombination events (red) between
the paternal genomes \textsf{e}
and \textsf{f}, and regions of genome inherited are shown.
Genomes are shaded such that where, backwards in time,
they merge into a common ancestor, the merged region is darker.
(B) The corresponding gARG along with inheritance annotations on all edges
(partial inheritance in bold).
(C) The corresponding local trees.
}
\end{figure}

As illustrated in Fig.~\ref{fig-arg-in-pedigree},
the gARG for a given set of individuals is embedded in their pedigree.
In this figure, diploid individuals are labelled $D_1, D_2...$, and
rather than denoting their constituent genomes using the natural numbers
we use lowercase alphabetical labels, to avoid confusion with genomic
positions. Individual $D_1$ is therefore composed
of two genomes \noderef{a} and \noderef{b}, which are inherited from its
two parents, $D_3$ and $D_4$. Each inherited genome may be the recombined product
of the genomes contained within a parent. In this example,
genome \noderef{b} was inherited directly from $D_4$'s genome \noderef{g} without
recombination, whereas
\noderef{a} is the recombinant product of
$D_2$'s two genomes \noderef{e} and \noderef{f} crossing over at position 2.
This recombination means \noderef{a} inherits the (half-closed) genome
interval $[0, 2)$ from \noderef{e} and $[2, 10)$ from \noderef{f}.
These intervals are shown attached to the corresponding graph edges.

@@

% NOTE: important to emphasise TWO things here, events and vagueness
% actual encoding mechanism (i.e. how trees fit into the ARG)
A common feature of these definitions is that they are expressed
in terms of evolutionary \emph{events}, and so for the purposes of
discussion we can label
this prevailing interpretation as an ``event ARG'', or eARG.
(Many definitions also emphasise
the necessity of exhaustively capturing \emph{all} events, which we
examine in later sections.)
Another common feature of these definitions is that they do not explicitly
discuss the mechanism by which genealogical trees vary along the genome.
The topology of an eARG defines the common ancestor and
recombination events that occurred,
but the graph structure alone is not sufficient to define the local trees,
or equivalently, how ``ancestral material'' (Section XXX) flows along
the edges of the ARG.
This is usually assumed to follow the mechanism described by
Griffiths and colleagues in which we have
two different ``types'' of node in the graph:
common ancestor nodes in which the inbound lineages are merged into a
single ancestral lineage with one parent, and recombination
nodes in which a single lineage is split into two independent
ancestral lineages.
Recombination nodes are then
annotated with
the corresponding crossover breakpoint~\citep{griffiths1996ancestral}.
Fig.~\ref{fig-event-arg} shows an example of a classical
eARG with three samples (\noderef{a}, \noderef{b}, and \noderef{c})
and a single recombination event, along with an example concrete
encoding of the data.  There is a single recombination event
at node \noderef{d} with a breakpoint at position $x$. We
assume that \noderef{d} inherits genetic material to the
left of $x$ from \noderef{e} and to the right of $x$ from \noderef{f}.
As shown in Fig.~\ref{fig-event-arg}B,
the local trees are embedded in the graph, and can be reconstructed
in essentially the same manner as outlined the previous section for
gARGs. The only difference is that decisions about which outbound
edge to follow during the rootward traversal are taken at recombination
nodes, following
either the common convention that the order of parents
is significant~\citep[e.g.][]{griffiths1991two},
or by incorporating additional information to
distinguish left and right parents
into the
encoding~\citep[e.g.][]{gusfield2014recombinatorics,ignatieva2021kwarg}.

@@

\end{tikzpicture}
\caption{\label{fig-event-arg}
A classical event ARG. (A) Standard graph depiction with
breakpoint $x$ associated with the recombination node \noderef{d}.
Nodes \noderef{e}, \noderef{f} and \noderef{g} are common ancestor events.
(B) Corresponding local trees to the left and right of breakpoint $x$
(note these are shown in the conventional form in which only coalescences
within the local tree are included; see section XXX for a discussion
of this important point).
(C) A concrete encoding of the information (right).
Recombination nodes have a non-null breakpoint
and two parents.
}
\end{figure}

Whether we regard nodes as events or genomes is something of a
philosophical question, and in most senses the two are equivalent
(but see the discussion on ``unary nodes'' in section XXX).
From a concrete data-structure encoding perspective, the only real
difference between an eARG and a gARG is that in an eARG we store recombination
\emph{breakpoints} at nodes of out-degree two (recombination nodes)
whereas in a gARG we store \emph{inheritance intervals} on edges.
A key advantage of associating inheritance intervals with
edges in a gARG is that it allows us to describe evolutionary events other
than simple crossovers, such as multiple recombinations and
gene-conversions. By explicitly stating the exact regions of genome
that are transmitted along an edge, we generalise the representation
to encompass any process that leads to the differential inheritance of
genetic material along the genome.

@@

Prospective ARGs arise in individual-based forwards-time
simulations~\citep{kelleher2018efficient,haller2018tree},
where the genetic inheritance between genomes is recorded
exhaustively and periodically
``simplified'' to retain only
the ancestry relevant to the current population.
\citet{kelleher2018efficient} refer to the structure
recording all such forwards-in-time genetic relationships
as an ``embellished pedigree`` (and suggest the term ``nedigree'' as a shorthand).
Describing this instead as a ``prospective ARG'', emphasising
the use of the same data structures and the direct connection with
the usual retrospective interpretation of an ARG, may be
more useful.
The ``simplify'' algorithm, which prunes away parts of the graph that
are not ancestral to a sample, is the key enabling factor for
this approach to forwards-time simulation and is
described in detail by
\citet{kelleher2018efficient}.
It is a powerful tool for simulation and analysis as it
allows efficient subsetting of ARGs, with the ability to
remove both samples and certain levels of detail about recombination,
as we discuss in the following sections.

@@

It is useful to have
a concrete definition and explicit process for local tree extraction.
We can describe a local tree as an
oriented tree~\cite[p.\ 461]{knuth11combinatorial},
a sequence of integers $\pi_1, \pi_2\dots$ where $\pi_u$ denotes the parent of
node $u$~\citep{kelleher2013coalescent,kelleher2014coalescent,kelleher2016efficient}.
If $u$ is a root
% I'm not sure if this reachability stuff is a helpful clarification, and whether it'll just
% confuse people. It depends on some tricky details.
(or not reachable from the samples)
in the local tree at position $x$, then $\pi_u = -1$ (by convention).
% JK: this confused some people, so best left out?
% Technically, this structure is a ``forest'', as it allows us to have
% multiple disconnected trees, which occurs when all samples have not
% found a most recent common ancestor.
Oriented trees allow nodes
to have  any number of children; from one (see the next section for more
discussion on such ``unary nodes''), to arbitrarily
large polytomies.
To recover the local tree $\pi$ at position $x$, we begin by
setting $\pi_u = -1$ for each $u\in N$. Then, for each sample
node in $S$ we trace its path rootwards through the
ARG for position $x$, and record this path in $\pi$.
Specifically, at a given node $u$,
we find an edge $(c, p, I) \in E$ such that $u = c$ and $x \in I$, and set
$\pi_c \leftarrow p$. We then set $u \leftarrow p$, and repeat
until either $\pi_u \neq -1$ (indicating we have traversed this section
of the ARG already on the path from another sample) or there
is no matching outbound edge (indicating we are at a root).

@@

The internal nodes of trees, however, are usually
considered to be \emph{unlabelled},
because they most often correspond
to anonymous hypothetical ancestors.
Internal ARG nodes likewise correspond to anonymous hypothetical
ancestors, but if we do not label them we lose the fact that
the \emph{same} ancestors persist across multiple trees.
Without labelled internal tree nodes,
we must infer their identity
from the tree topology, which is both
expensive to compute and imprecise. For example
using only the tree topologies it would not be straightforward to
infer that node \noderef{i} in the first and last trees of
Fig.~\ref{fig-arg-in-pedigree}C is the same node.
\cite{shipilina2023origin} discuss the same ideas,
and note that the
``full ARG...~contains more information than the series of tree
sequences along the genome''.
Their statement that an ARG
contains more information than its local trees is true only if
the local trees are unlabeled and/or do not contain unary nodes
(see the next section for discussion on this point).
However, if the local trees
contain labelled internal nodes,
then  there is precisely as
much information in them as an ARG.

@@

\section*{Locally unary nodes}
The arity of a node is the number of child nodes it has. There is an
important distinction between the number of children a node has
in the graph and the number of children it has in the local trees,
because a (graph) child node is only a child in the local tree for position
$x$ if $x$ is in the inheritance interval for the corresponding edge.
Thus, for a given node $u$ and a genome position $x$ the arity
of $u$ in that local tree is less than or equal to the graph arity of
$u$. The arity
of a node in the local trees can therefore change as we move along
the genome.

This distinction between graph and local tree arity is mainly
of interest when we consider \emph{unary} nodes, those that have
a single child.
Returning to the example in Fig~\ref{fig-arg-in-pedigree}, nodes
\noderef{g} and \noderef{h} are graph-unary, and are consequently
also unary in the local trees.
On the other hand, node \noderef{f} has two children
in the graph (Fig~\ref{fig-arg-in-pedigree}B), but is only binary
in the local tree covering the interval $[2, 7)$,
representing the coalescence of samples \noderef{a} and \noderef{c}
in this region of genome. Over the interval $[0, 2)$ no coalescence occurs,
but we still record the fact that genome \noderef{c} inherits from \noderef{f}
in the local tree. Thus, \noderef{c} has a single child in this
interval and it is unary in this local tree.
In another example, \noderef{e} is binary in the graph, but is
unary in each of the local trees it is present in.
This is because \noderef{a} and \noderef{c} are both recombinant
offspring of \noderef{e} and \noderef{f}, and,
in this example,
\noderef{a} inherits from
\noderef{e} over the interval $[0, 2)$,
and \noderef{c} inherits from \noderef{e} over $[7, 10)$.
The intervals over which
we know that a node inherits from another, but where there
is no local coalescence, are marked by unary nodes in the
local trees.

Outside of the context of simulation, graph-unary nodes are
only like to occur in longitudinal datasets where genetic
data is sampled at many timepoints and recombination
is rare (e.g.~SARS-Cov-2; see Discussion).
\emph{Locally} unary nodes, those which have one child
in one or more local trees, are a common and important feature
of many different types of ARG, and a recurring topic
in this article. Without these nodes marking the passage
of ancestral material through specific ancestors, the local trees
lack information about events other than local coalescence.
% Not sure if switching example will confuse people here, but would
% like to contrast with example where we don't use unary nodes to
% emphasise the point that we lose info
For example, the local trees for the classical event ARG
depicted in Fig.~\ref{fig-event-arg}B follow the usual conventions
and do not include any information about the recombination
that occurred at node \noderef{d}. Given these two local trees
in isolation
% (without further information about the corresponding ARG)
we lack specific information about the recombination.
Explicitly recording that node \noderef{d} lies on the
branch joining \noderef{b} to \noderef{e} in the left hand
tree, and \noderef{b} to \noderef{f} in the right hand tree
resolves all ambiguity, and makes the collection of local
trees exactly equivalent to the corresponding ARG (see previous section).
Unary nodes are a vital link between ARGs and local trees, and we
cannot fully reason about how a local tree is embedded in an ARG
without them.

@@

\begin{figure}[t]
\centering
% FIXME this is a quick nasty hack to make the figure a bit smaller and
% prevent flushing all the other figures to the end of the document.
\scalebox{0.54}{
\begin{tabular}{cc}
\begin{tikzpicture}
	\node [anchor=north west] at (-3.5,9.3) {\LARGE \textbf{A}};
	\draw (-0.4, -0.2) -- (0.4, -0.2) -- (0.4, -0.3) -- (-0.4, -0.3) -- (-0.4, -0.2);
	\draw (-0.1, -0.1) -- (-0.1, -0.4);
	\node [label=below:{\small $v$}] at (-0.1, -0.2) {};
	\draw (3.6, -0.2) -- (4.4, -0.2) -- (4.4, -0.3) -- (3.6, -0.3) -- (3.6, -0.2);
	\draw (5.6, -0.2) -- (6.4, -0.2) -- (6.4, -0.3) -- (5.6, -0.3) -- (5.6, -0.2);
